Evolutionary stretegies

### 2016-01-23 evolutionaryComputation/summery.tex
space!
sumerizing....

\section{ES representation}
Fitness function: $f(x_1,\dots,x_n):\mathbb{R}^n\to \mathbb{R}$.
Genotype representation of an individual solution:
$(x_1,\dots,x_n,\sigma^2_1,\dots,\sigma^2_n, c_{12},\dots,c_{n-1,n})$,
paremeters $(x_1, \dots,x_n)$ need to be optimized.
Individiual solution consists of 3 parts: $\vec{x}$: problem vairables
$\Rightarrow$ Fitness $f(\vec{x})$. $\vec{sigma}$: standard deviations
$\Rightarrow$ variances. $\vec{\alpha}$: rotation angles $\Rightarrow$
covariances.

>>>>

\section{ES representation}
Fitness function: $f(x_1,\dots,x_n):\mathbb{R}^n\to \mathbb{R}$.
Genotype representation of an individual solution:
$(x_1,\dots,x_n,\sigma^2_1,\dots,\sigma^2_n, c_{12},\dots,c_{n-1,n})$,
paremeters $(x_1, \dots,x_n)$ need to be optimized.
Individiual solution consists of 3 parts: $\vec{x}$: problem vairables
$\Rightarrow$ Fitness $f(\vec{x})$. $\vec{sigma}$: standard deviations
$\Rightarrow$ variances. $\vec{\alpha}$: rotation angles $\Rightarrow$
covariances. The $n$-dimensional normal probability density function:
$p(X=x_1,\dots,x_n)=\frac{exp(-\frac{1}{2}X^TC^{-1}X)}{\sqrt{(2\pi)^n|C|}}$.
$C$: correlation matrix ($c_{ij}$; $|C|$ determinant $\Rightarrow$ rotation 
angles $\alpha_{ij}$: tan $2\alpha_{ij}=2c_{ij}/(\sigma^2_i-\sigma^2_j)$.
1-dimensional gaussian function:
$f(x)=\frac{1}{\sqrt{2\pi \sigma^2}}exp\frac{(x-\mu)^2}{2\sigma^2}$
\subsection{Mutation}
Complete covairance matrix: $\sigma_1,\dots,\sigma_n$; $c_{ij}\neq 0 (i\neq j)$.
The strategy paremeters are mutated:
$\sigma'_i=\sigma_ie^{
	\frac{\mathbb{N}(0,1)}{\sqrt{2n}}+
	\frac{\mathbb{N}_i(0,1)}{\sqrt{2\sqrt{n}}}
}$
$\alpha'_j=\alpha_j+\beta\mathbb{N}_j(0,1)$.
$\beta = 5$ degree in radians. $\mathbb{N}(0,1)$: standard normal
distribution. Then the problem paremeters are mutated with the new
strategy: $\vec{x}'=\vec{x}+\vec{N}(\vec{0},\vec{\sigma},\vec{\alpha}')$.
$\vec{N}$: n-dimensional normal distribution.
Often this is simplified by not doing angles or even just having a single
standard deviation (ie no index at $\sigma$ and nothing after the + 
in the power $e$).
\subsection{Recombination}
create one offspring from several parents selected randomly. Problem parameters
are averaged. The std devation is selected from one of the parents. Rotation
angles are not recombined
\subsection{Selection}
ES applies a high selection pressure: from $\mu$ parents $\lambda$ offspring
are generated with $\lambda >> \mu$ (~5 to 10 times). The best $\mu$ solutions
of the $\lambda$ offspring are selected, (or from both offspring and parents,
but experiments show just offspring has better selfadaptation).
